\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-11-11 tex/gitlinks.tex
bugfix

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/183ebfe9e8b50599ac94eec0b58c35cbed8bce63/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/183ebfe9e8b50599ac94eec0b58c35cbed8bce63/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/183ebfe9e8b50599ac94eec0b58c35cbed8bce63/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/3e02de349ee1df17319a412d32355b7ceaeff3dd/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/3e02de349ee1df17319a412d32355b7ceaeff3dd/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/3e02de349ee1df17319a412d32355b7ceaeff3dd/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

### 2020-11-11 tex/ms.tex
bugfix

\section{The Size and Contrast Integrals}
\label{sec:size-contrast}

\section{The Latitude and Longitude Integrals}
\label{sec:lat-lon}
%
Our goal in this section is to compute the integrals...

@@

>>>>

\section{The Size Integral}
\label{sec:size}
%
\xxx{Coming soon.}

\section{The Latitude and Longitude Integrals}
\label{sec:lat-lon}
%
Our goal in this section is to compute the first and second moments
of the latitude ($\mathbf{e}_\phi$, $\mathbf{E}_\phi$)
and longitude ($\mathbf{e}_\lambda$, $\mathbf{E}_\lambda$) distributions
(Equations \ref{eq:e2}, \ref{eq:e3}, \ref{eq:E2}, and \ref{eq:E3},
respectively). These involve integrals over the terms in the Wigner
rotation matrix for spherical harmonics, which we discuss below.

@@

\subsubsection{Second moment}
%
We write the second moment integral as
%
\begin{proof}{}
    \mathbf{E}_\lambda
    & \equiv
    \int
    \mathbf{R}_{\hat{\mathbf{y}}}(\lambda) \,
    \mathbf{E}_\phi \,
    \mathbf{E}_\phi^\top \,
    \mathbf{R}_{\hat{\mathbf{y}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \nonumber
    \\
    %
    & =
    %
    \setstackgap{L}{1.25\baselineskip}
    \fixTABwidth{T}
    \parenMatrixstack{
    \mathbf{E}_\lambda^{0,0} & \mathbf{E}_\lambda^{0,1} & \mathbf{E}_\lambda^{0,2} & \cdots & \mathbf{E}_\lambda^{0,l_{\mathrm{max}}} \\
    \mathbf{E}_\lambda^{1,0} & \mathbf{E}_\lambda^{1,1} & \mathbf{E}_\lambda^{1,2} & \cdots & \mathbf{E}_\lambda^{1,l_{\mathrm{max}}} \\
    \mathbf{E}_\lambda^{2,0} & \mathbf{E}_\lambda^{2,1} & \mathbf{E}_\lambda^{2,2} & \cdots & \mathbf{E}_\lambda^{2,l_{\mathrm{max}}} \\
    \vdots & \vdots & \vdots & \ddots & \vdots \\
    \mathbf{E}_\lambda^{l_{\mathrm{max}},0} & \mathbf{E}_\lambda^{l_{\mathrm{max}},1} & \mathbf{E}_\lambda^{l_{\mathrm{max}},2} & \cdots & \mathbf{E}_\lambda^{l_{\mathrm{max}},l_{\mathrm{max}}}
    }
    \quad,
\end{proof}
%
where
%
\begin{proof}{}
    \mathbf{E}_\lambda^{l,l'}
    & =
    \int
    \mathbf{R}^l_{\hat{\mathbf{y}}}(\lambda) \,
    \mathbf{E}^l_\phi \,
    {\mathbf{E}^l_\phi}^\top \,
    {\mathbf{R}^{l'}_{\hat{\mathbf{y}}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \nonumber \\
    %
    & =
    %
    {\mathbf{U}^l}^{-1}
    \mathbf{P}^l_\lambda
    {{\mathbf{U}^l}^{-1}}^\top
\end{proof}
%
and we define
%
\begin{align}
    \label{eq:Pllam}
    \mathbf{P}^l_\lambda
     & \equiv
    \int
    \mathbf{D}^l_{\hat{\mathbf{x}}}(\lambda) \,
    \bar{\mathbf{E}}^l_\phi \,
    {\mathbf{D}^l_{\hat{\mathbf{x}}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \\
    \bar{\mathbf{E}}^l_\phi
     & \equiv
    \mathbf{U}^l
    \mathbf{E}^l_\phi
    {\mathbf{E}^l_\phi}^\top
    {\mathbf{U}^l}^\top
    \quad.
\end{align}
%
We then express the terms of $\mathbf{P}^l_\lambda$ as
%
\begin{align}
    {P^l_\lambda}_{m,m'}
     & =
    \int
    \sum\limits_{\mu=-l}^l
    \sum\limits_{\nu=-l}^l
    {D^l_{\hat{\mathbf{x}}}}_{m,\mu}(\lambda) \,
    {\bar{E}^l}{{}_\phi}_{\mu,\nu} \,
    {D^l_{\hat{\mathbf{x}}}}_{\nu,m'}(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    %
    \nonumber \\[0.5em]
    %
     & =
    \sum\limits_{\mu=-l}^l
    \sum\limits_{\nu=-l}^l
    {\bar{E}^l}{{}_\phi}_{\mu,\nu}
    \sum\limits_{i=0}^{2l}
    \sum\limits_{j=0}^{2l}
    c_{m,\mu,i}^{l}
    c_{\nu,m',j}^{l}
    \,
    {Q^l_\lambda}_{i,j}
    \quad,
\end{align}
%
where
%
\begin{proof}{}
    {Q^l_\lambda}_{i,j}
    & \equiv
    \frac{1}{2\pi}
    \int_{-\pi}^{\pi}
    %
    \mathrm{sgn}(\sin\lambda)^{i+j}
    (1 - \cos\lambda)^{2l - \frac{i+j}{2}}
    (1 + \cos\lambda)^\frac{i+j}{2}
    %
    \,
    \mathrm{d}\lambda
    \nonumber \\[0.5em]
    %
    & =
    %
    \begin{cases}
        \dfrac{2^{2l} \Gamma \left(\frac{1+i+j}{2}\right)
            \Gamma \left(2l+\frac{1-i-j}{2}\right)}{\pi  \Gamma (2l+1)}
        %
         & i+j \,\, \mathrm{even}
        %
        \\
        %
        0
        %
         & i+j \,\, \mathrm{odd} \quad,
    \end{cases}
\end{proof}
%
whose terms may again be computed by upward recursion.

\section{The Contrast Integral}
\label{sec:contrast}
%
\xxx{Coming soon.}
